ACNP 2024 MS ANXIETY

### 2024-09-03 scripts/FINAL_scripts_clean/MSAnxiety_manuscript_post_replication_prop_FINAL.Rmd
Add files via upload

prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot_bar <-  ggplot(df_mean_UF_mean_by_anxiety_severity, aes(x=anxiety_severity, y=mean_UF_mean, fill=anxiety_severity)) +
  geom_bar(stat="identity", width = .6) +  
  geom_errorbar(aes(ymin = mean_UF_mean - sem_UF, ymax = mean_UF_mean + sem_UF), width = 0.2, size = 0.8)  +
  scale_fill_viridis(discrete = TRUE, option = "D") +  # Use Viridis color scale
  ylim(0,45)+
  theme(axis.text.x = element_text(size=12, colour = "black"),
        axis.text.y = element_text(size=12, colour = "black"),
        axis.title.y = element_text(size=16, colour = "black"),
        axis.title.x = element_blank(),
        axis.line = element_line(linewidth = 1.5, colour="black"),
        legend.position = "none",
        panel.background = element_rect(colour = "white", fill = "white")) + 
  labs(y = "Percent (%) of Uncinate Injured")
prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot_bar

@@

@@

# Create the plot with narrower violins and error bars
prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot <- ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x = anxiety_severity, y = mean_UF_prop, fill = anxiety_severity)) +
  geom_violin(width = 0.6, alpha =1.5, color = "black", trim = FALSE) +  # Adjust violin width and transparency
  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
  ylim(0,100) +
  #geom_errorbar(aes(ymin = mean_UF_prop - sem_UF_prop, ymax = mean_UF_prop + sem_UF_prop), width = 0.2, color = "black") +  # Add error bars
  scale_fill_viridis(discrete = TRUE, option = "D") +  # Use Viridis color scale
  #theme_minimal(base_size = 14) +  # Use a minimal theme with a base font size
  theme(
    axis.text.x = element_text(size = 12, colour = "black"),  # Rotate x-axis labels for better readability
    axis.text.y = element_text(size = 12, colour = "black"),
    axis.title.y = element_text(size = 16, colour = "black"),
    axis.title.x = element_blank(),
    axis.line = element_line(linewidth = 1.5, colour = "black"),
    legend.position = "none",
    panel.background = element_rect(colour = "white", fill = "white"),
    plot.margin = margin(10, 10, 10, 10)  # Add margins around the plot
  ) + 
  labs(y = "Percent (%) of Uncinate Injured")

@@

# Create the plot with narrower violins, viridis colors, and horizontal lines at means
prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot <- ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x = anxiety_severity, y = mean_UF_prop, color = anxiety_severity)) +
  geom_point(position = position_jitter(.1), size = 2, alpha = 0.8) +  # Add points with jitter using viridis colors
  stat_summary(fun = "mean", geom = "crossbar", width = 0.3, color = "black", size = 0.5) +  # Add horizontal lines at means
  scale_color_viridis(discrete = TRUE, option = "D") +  # Use Viridis color scale for points
  theme(
    axis.text.x = element_text(size = 12, colour = "black"),  # X-axis labels
    axis.text.y = element_text(size = 12, colour = "black"),  # Y-axis labels
    axis.title.y = element_text(size = 16, colour = "black"),  # Y-axis title
    axis.title.x = element_blank(),  # Remove X-axis title
    axis.line = element_line(linewidth = 1.5, colour = "black"),  # Axis lines
    legend.position = "none",  # Remove legend
    panel.background = element_rect(colour = "white", fill = "white")  # Background
  ) + 
  labs(y = "Percent (%) of Uncinate Injured")  # Y-axis label

@@

>>>>

prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot_bar <-  ggplot(df_mean_UF_mean_by_anxiety_severity, aes(x=anxiety_severity, y=mean_UF_mean, fill=anxiety_severity)) +
  geom_bar(stat="identity", width = .6) +  
  geom_errorbar(aes(ymin = mean_UF_mean - sem_UF, ymax = mean_UF_mean + sem_UF), width = 0.2, size = 0.8)  +
  scale_fill_viridis(discrete = TRUE, option = "D", direction = -1) +  # Use Viridis color scale
  ylim(0,45)+
  theme(axis.text.x = element_text(size=12, colour = "black"),
        axis.text.y = element_text(size=12, colour = "black"),
        axis.title.y = element_text(size=16, colour = "black"),
        axis.title.x = element_blank(),
        axis.line = element_line(linewidth = 1.5, colour="black"),
        legend.position = "none",
        aspect.ratio = 7/5,
        panel.background = element_rect(colour = "white", fill = "white")) + 
  labs(y = "Percent (%) of Uncinate Injured")
prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot_bar

@@

### try horizontal
prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot_bar_horiz <-  ggplot(df_mean_UF_mean_by_anxiety_severity, aes(y=anxiety_severity, x=mean_UF_mean, fill=anxiety_severity)) +
  geom_bar(stat="identity", width = .6) +  
  geom_errorbar(aes(xmin = mean_UF_mean - sem_UF, xmax = mean_UF_mean + sem_UF), width = 0.2, size = 0.8)  +
  scale_fill_viridis(discrete = TRUE, option = "D", direction = -1) +  # Use Viridis color scale
  xlim(0,45)+
  theme(axis.text.x = element_text(size=12, colour = "black"),
        axis.text.y = element_text(size=12, colour = "black"),
        axis.title.x = element_text(size=16, colour = "black"),
        axis.title.y = element_blank(),
        axis.line = element_line(linewidth = 1.5, colour="black"),
        legend.position = "none",
        aspect.ratio = 7/5,
        panel.background = element_rect(colour = "white", fill = "white")) + 
  labs(x = "Percent (%) of Uncinate Injured")
prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot_bar_horiz

@@

# Create the plot with narrower violins and error bars
prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot <- ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x = anxiety_severity, y = mean_UF_prop, fill = anxiety_severity)) +
  geom_violin(width = 0.5, alpha =.5, color = "black", trim = FALSE) +  # Adjust violin width and transparency
  stat_summary(fun = "mean", geom = "crossbar", width = 0.3, color = "black", size = 0.5) +  # Add horizontal lines at means
  #geom_point(position = position_jitter(seed = 1, width = 0.2)) +

#  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
  ylim(0,100) +
  #geom_errorbar(aes(ymin = mean_UF_prop - sem_UF_prop, ymax = mean_UF_prop + sem_UF_prop), width = 0.2, color = "black") +  # Add error bars
  scale_fill_viridis(discrete = TRUE, option = "D", direction = -1) +  # Use Viridis color scale
  #theme_minimal(base_size = 14) +  # Use a minimal theme with a base font size
  theme(
    axis.text.x = element_text(size = 12, colour = "black"),  # Rotate x-axis labels for better readability
    axis.text.y = element_text(size = 12, colour = "black"),
    axis.title.y = element_text(size = 16, colour = "black"),
    axis.title.x = element_blank(),
    axis.line = element_line(linewidth = 1.5, colour = "black"),
    legend.position = "none",
    panel.background = element_rect(colour = "white", fill = "white"),
    plot.margin = margin(10, 10, 10, 10),  # Add margins around the plot
    aspect.ratio = 5/5
  ) + 
  labs(y = "Percent (%) of Uncinate Injured")

@@

# Create the plot with narrower violins, viridis colors, and horizontal lines at means
prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot <- ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x = anxiety_severity, y = mean_UF_prop, color = anxiety_severity)) +
  geom_point(position = position_jitter(width=.1, height = 0), size = 2, alpha = 0.8) +  # Add points with jitter using viridis colors
  stat_summary(fun = "mean", geom = "crossbar", width = 0.3, color = "black", size = 0.5) +  # Add horizontal lines at means
  scale_color_viridis(discrete = TRUE, option = "D", direction = -1) +  # Use Viridis color scale for points
  theme(
    axis.text.x = element_text(size = 12, colour = "black"),  # X-axis labels
    axis.text.y = element_text(size = 12, colour = "black"),  # Y-axis labels
    axis.title.y = element_text(size = 16, colour = "black"),  # Y-axis title
    axis.title.x = element_blank(),  # Remove X-axis title
    axis.line = element_line(linewidth = 1.5, colour = "black"),  # Axis lines
    legend.position = "none",  # Remove legend
    panel.background = element_rect(colour = "white", fill = "white")  # Background
  ) + 
  labs(y = "Percent (%) of Uncinate Injured")  # Y-axis label

@@

##### Box plot with jitter ND OTHERS
```{r box_jitter}
#### trying prettier things
df_disease_burden_unc_and_anx_net_collapsed_variables <- df_demo_and_fascicles %>%
  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
  filter(anxiety_dose != -1) %>%
  mutate(anxiety_severity = ifelse(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed == "true_healthy", "MS+noA", 
                                   ifelse(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed == "Has.Anxietydx.OR.Antianxiety.Meds", "MS+mildA", "MS+severeA"))) %>% 
  mutate(anxiety_severity = factor(anxiety_severity, levels = c("MS+noA", "MS+mildA", "MS+severeA"))) %>%
  mutate(mean_UF_prop = mean_UF_prop*100)

##BOX PLOT WITH JITTER
prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot <- ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x = anxiety_severity, y = mean_UF_prop, color = anxiety_severity)) +
  geom_boxplot(aes(fill = anxiety_severity), alpha = 0.3, outlier.size = 0) +  # Add boxplots with some transparency
  geom_jitter(width = 0.2, size = 2, alpha = 0.8) +  # Add jittered points for individual observations
  scale_color_viridis(discrete = TRUE, option = "D") +  # Use Viridis color scale
  scale_fill_viridis(discrete = TRUE, option = "D") +
  theme(
    axis.text.x = element_text(size = 12, colour = "black"),
    axis.text.y = element_text(size = 12, colour = "black"),
    axis.title.y = element_text(size = 16, colour = "black"),
    axis.title.x = element_blank(),
    axis.line = element_line(linewidth = 1.5, colour = "black"),
    legend.position = "none",
    panel.background = element_rect(colour = "white", fill = "white")
  ) + 
  labs(y = "Percent (%) of Uncinate Injured")

##### BOX PLOT NO JITTER
prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot <- ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x = anxiety_severity, y = mean_UF_prop, color = anxiety_severity)) +
  geom_boxplot(aes(fill = anxiety_severity), alpha = 0.3, outlier.size = 0) +  # Add boxplots with some transparency
#  geom_jitter(width = 0.2, size = 2, alpha = 0.8) +  # Add jittered points for individual observations
  scale_color_viridis(discrete = TRUE, option = "D") +  # Use Viridis color scale
  scale_fill_viridis(discrete = TRUE, option = "D") +
  theme(
    axis.text.x = element_text(size = 12, colour = "black"),
    axis.text.y = element_text(size = 12, colour = "black"),
    axis.title.y = element_text(size = 16, colour = "black"),
    axis.title.x = element_blank(),
    axis.line = element_line(linewidth = 1.5, colour = "black"),
    legend.position = "none",
    panel.background = element_rect(colour = "white", fill = "white")
  ) + 
  labs(y = "Percent (%) of Uncinate Injured")

###dot plot
prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot <- ggplot(df_disease_burden_unc_and_anx_net_collapsed_variables, aes(x = anxiety_severity, y = mean_UF_prop, color = anxiety_severity)) +
  geom_point(position = position_jitter(width = 0.2, height = 0), size = 2, alpha = 0.8) +  # Individual data points with jitter
  stat_summary(fun = "mean", geom = "point", size = 4, shape = 21, fill = "black") +  # Mean points
  stat_summary(fun.data = mean_cl_normal, geom = "errorbar", width = 0.2, color = "black") +  # Confidence intervals
  scale_color_viridis(discrete = TRUE, option = "D") +
  theme(
    axis.text.x = element_text(size = 12, colour = "black"),
    axis.text.y = element_text(size = 12, colour = "black"),
    axis.title.y = element_text(size = 16, colour = "black"),
    axis.title.x = element_blank(),
    axis.line = element_line(linewidth = 1.5, colour = "black"),
    legend.position = "none",
    panel.background = element_rect(colour = "white", fill = "white")
  ) + 
  labs(y = "Percent (%) of Uncinate Injured")

### bar with error
summary_stats <- df_disease_burden_unc_and_anx_net_collapsed_variables %>%
  group_by(anxiety_severity) %>%
  summarize(mean_UF_prop = mean(mean_UF_prop, na.rm = TRUE),
            sd_UF_prop = sd(mean_UF_prop, na.rm = TRUE),
            n = n(),
            se_UF_prop = sd_UF_prop / sqrt(n))

prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot <- ggplot(summary_stats, aes(y = anxiety_severity, x = mean_UF_prop, fill = anxiety_severity)) +
  geom_bar(stat = "identity", position = position_dodge(), width = 0.7) +  # Bar plot
  geom_errorbar(aes(xmin = mean_UF_prop - se_UF_prop, xmax = mean_UF_prop + se_UF_prop), width = 0.2) +  # Error bars
  scale_fill_viridis(discrete = TRUE, option = "D") +
  theme(
    axis.text.x = element_text(size = 12, colour = "black"),
    axis.text.y = element_text(size = 12, colour = "black"),
#    axis.title.y = element_text(size = 16, colour = "black"),
    axis.title.y = element_blank(),
    axis.line = element_line(linewidth = 1.5, colour = "black"),
    legend.position = "none",
    panel.background = element_rect(colour = "white", fill = "white")
  ) + 
  labs(x = "Percent (%) of Uncinate Injured")

# Display the plot
prop_injured_mean_uncinate_by_anxiety_burden_collapsed_vars_plot
```
